---
title: "Parking_JFK"
author: "Christopher Eshleman"
date: "5/25/2019"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Aiport Parking at JFK

```{r, include=FALSE, echo=FALSE}

library(leaps) 
library(zoo) 
library(olsrr) 
library(glmnet) 
library(lubridate) 
library(ISLR) 
library(broom) 

oldw = getOption("warn")
options(warn = -1)


setwd("~/Dropbox/Work and research/Port Authority/airport_parking")
```

Load data on airport parking activity, ticket prices and consumer spending. 

```{r, echo=FALSE, include=FALSE}
a = read.csv("./Avg_Domestic_Ticket_Prices.csv") 
a$Year = as.numeric(as.character(a$Year)) 
a$quarter = paste0("0", a$Quarter)
a$quarter = as.Date(paste(a$Year,paste0("0", a$Quarter),"01",sep="-")) 
a = subset(a,a$quarter>="2009-01-01") 
b = read.csv("./EWR_Data.csv") 
c = read.csv("./JFK_Data.csv") 
d = read.csv("./Consumer_Spending.csv") 
dd = read.csv("./Consumer_Spending_short.csv") 
c$month = as.Date(c$month, format="%m/%d/%y") 
d$month = as.Date(d$month, format="%m/%d/%y") 
cd = merge(c,d, by="month",all.x=TRUE) 
cd$Year = NULL 
cd$Month = NULL 
cd$m = month(cd$month) 
cd$quarter = substr(quarters(cd$month), 2, 2)
cd$yr = year(cd$month) 
cd$quarter = paste(year(cd$month),cd$quarter,sep="-") 
cd$m = NULL 
cd$q = NULL 
cd$yr = NULL 

cd = aggregate(. ~ quarter, cd, FUN = mean, na.action=na.pass) 
cd$q = seq(as.Date("2006/1/1"), as.Date("2019/1/1"), by = "quarter")
cd = subset(cd,cd$q<"2018-04-01") 

names(dd) = tolower(names(dd)) 
dd$month = as.Date(dd$month, format="%m/%d/%y") 
cdd = merge(c,dd,by="month") 

cdd$m = month(cdd$month) 
cdd$quarter = substr(quarters(cdd$month), 2, 2)
cdd$yr = year(cdd$month) 
cdd$quarter = paste(year(cdd$month),cdd$quarter,sep="-") 
cdd$m = NULL 
cdd$q = NULL 
cdd$yr = NULL 
cdd = aggregate(. ~ quarter, cdd, FUN = mean, na.action=na.pass) 
cdd$q = seq(as.Date("2006/1/1"), as.Date("2019/1/1"), by = "quarter")
cdd = subset(cdd,cdd$q<"2018-04-01") 
```

Remove things with too many blanks (NAs) and factor variables. 

```{r, echo=FALSE, include=FALSE} 
cdd2 = cdd[ , colSums(is.na(cdd)) == 0] 
cdd2 = cdd2[, !sapply(cdd2, is.character)] 
cdd2$Month = NULL 
cdd2$Year = NULL 
cdd2$month = NULL 
cdd2$q = NULL 
cdd2$Total.Revenue = NULL 
cdd2$Avg..Parking.Paid = NULL 
```

## Variable selection 
When running remember to remove id column, response column, factors, anything with too many NAs. 

First, check for strong correlations.

```{r, echo=FALSE}
#plot(cdd2)
#Redo this with some ggplot correlation matrix or something. 
```

# 1. Kitchen sink (less useful) 
```{r, echo=FALSE}
sink = lm(Paid.Parking.Activity ~ ., data=cdd2) 
sink.tidy = tidy(sink) 
sink.tidy2 = tidy(glance(sink)) 
sink.tidy 
```

# 2. Stepwise 
```{r, echo=FALSE}
  # 2a. p-values 
sink = lm(Paid.Parking.Activity ~ ., data=cdd2) 
sink_p = ols_step_backward_p(sink) 
sink_p 

  # 2b. AIC 
sink_aic = ols_step_backward_aic(sink)
sink_aic 
```

# 3. Lasso 
```{r, echo=FALSE}
y = cdd2[,1]
X = data.matrix(cdd2[,-c(1)], rownames.force = NA) 
fit.lasso = glmnet(x = X, y = y, alpha = 1, standardize=T) # alpha = 1 is lasso 
lasso.tidy = tidy(fit.lasso) 
lasso.tidy2 = tidy(glance(fit.lasso)) 
plot(fit.lasso, xvar = "lambda") 
coef(fit.lasso, s = .6) # s is the value of lambda 

options(warn = oldw)
```

Stepwise guidance suggests sticking with international emplanements and goods, and personal consumption is close.

```{r, echo=FALSE}
#time = auto.arima(ts(Put Y here),xreg=(put matrix of covariates here), ic="aic", trace=TRUE, allowdrift=FALSE)#,lambda=0, seasonal=TRUE)# 
#summary(fit) 
```
